% -------------------------------------------------------------------------------
%	SECTION TITLE
% -------------------------------------------------------------------------------
\cvsection{Experience}


% -------------------------------------------------------------------------------
%	CONTENT
% -------------------------------------------------------------------------------
\begin{cventries}

  % ---------------------------------------------------------
  \cventry
  {Postdoctoral Researcher} % Job title
  {Department of Biophysics, Kyoto University} % Organization
  {Kyoto, Japan} % Location
  {Jul. 2014 - PRESENT} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed a new method to incorporate bioinformatical results into
        coarse-grained molecular dynamics simulations to model protein-DNA binding
        specificity.}
    \item {Investigated polaron-like dynamic couplings among protein binding to
        DNA, protein sliding on DNA, and DNA bending by applying a coarse-grained
        simulation method to the bacterial architectural protein HU and 14 other
        DNA-binding proteins.}
    \end{cvitems}
  }

  % ---------------------------------------------------------
  \cventry
  {Graduate Student \& Research Assistant} % Job title
  {Institute of Biophysics, Nanjing University} % Organization
  {Nanjing, China} % Location
  {Sep. 2007 - Jun. 2014} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Explored water-mediated coordination of Ca$^{2+}$ ions and the
        allosteric conformational transitions in the EF-hand domains of Calmodulin with
        well-tempered bias-exchange metadynamics.}
    \item {Studied localized frustration and binding-induced conformational
        changes in the recognition of 5S rRNA by TFIIIA zinc-fingers using atomic MD
        simulations and MM-PB/GBSA analysis methods.}
    \item {Investigated the low folding cooperativity of protein HP35 using
        steered molecular dynamics simulations.  The results were combined with atomic
        force microscopy experiments to illustrate the folding mechanism of HP35.}
    \end{cvitems}
  }


  % ---------------------------------------------------------
\end{cventries}
