% -------------------------------------------------------------------------------
%	SECTION TITLE
% -------------------------------------------------------------------------------
\cvsection{Publication}


% -------------------------------------------------------------------------------
%	CONTENT
% -------------------------------------------------------------------------------
\begin{cventries}

  % ---------------------------------------------------------
  \cventry{}{}{}{}{
    % \footnotesize{
    % \begin{itemize}[itemsep=0.5em]
    \begin{cvitems} % Description(s) bullet points
    \item \textbf{Cheng Tan}, Tsuyoshi Terakawa and Shoji Takada. \\
      {\color{awesome} Dynamic Coupling among Protein Binding, Sliding, and DNA Bending Revealed by
      Molecular Dynamics.} \\
      \textit{J. Am. Chem. Soc.}, \textbf{2016}, 138(27), 8512-8522. \\[-6pt]
    \item Shoji Takada, Ryo Kanada, \textbf{Cheng Tan}, Tsuyoshi Terakawa, Wenfei
      Li and Hiroo Kenzaki. \\
      {\color{awesome} Modeling Structural Dynamics of Biomolecular Complexes by Coarse-Grained
      Molecular Simulations.} \\
      \textit{Acc. Chem. Res.}, \textbf{2015}, 48(12), 3026-3035. \\[-6pt]
    \item Yunqiang Bian, \textbf{Cheng Tan}, Jun Wang, Yuebiao Sheng, Jian Zhang and
      Wei Wang. \\
      {\color{awesome} Atomistic Picture for the Folding Pathway of a Hybrid-1 Type Human Telomeric
      DNA G-Quadruplex.} \\
      \textit{PLoS Comput. Biol.}, \textbf{2014}, 10(4), e1003562. \\[-6pt]
    \item \textbf{Cheng Tan}, Wenfei Li and Wei Wang.\\
      {\color{awesome} Localized Frustration and Binding-Induced Conformational Change in Recognition
      of 5S RNA by TFIIIA Zinc Finger.} \\
      \textit{J. Phys. Chem. B}, \textbf{2013}, 117(50), 15917--15925. \\[-6pt]
    \item \textbf{Cheng Tan}, Wenfei Li, and Wei Wang.\\
      {\color{awesome} Specific Binding of a Short miRNA Sequence by Zinc Knuckles of Lin28: A
      Molecular Dynamics Simulation Study.} \\
      \textit{J. Theor. Comput. Chem.}, \textbf{2013}, 12(8), 1341015. \\[-6pt]
    \item Chunmei Lv, \textbf{Cheng Tan}, Meng Qin, Dawei Zou, Yi Cao, and Wei Wang.\\
      {\color{awesome} Low Folding Cooperativity of HP35 Revealed by Single-Molecule Force
      Spectroscopy and Molecular Dynamics Simulation.} \\
      \textit{Biophys. J.}, \textbf{2012}, 102(8), 1944--1951. \\[-6pt]
      % \end{itemize}
    \end{cvitems}
    % }
    %   \normalsize{}
  }
  % ---------------------------------------------------------

\end{cventries}
