%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publication}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\begin{itemize}
\item \textbf{Cheng Tan}, Tsuyoshi Terakawa and Shoji Takada. \\
  Dynamic Coupling among Protein Binding, Sliding, and DNA Bending Revealed by
  Molecular Dynamics. \\
  \textit{J. Am. Chem. Soc.}, \textbf{2016}, 138(27), 8512-8522.
\item Shoji Takada, Ryo Kanada, \textbf{Cheng Tan}, Tsuyoshi Terakawa, Wenfei
  Li and Hiroo Kenzaki. \\
  Modeling Structural Dynamics of Biomolecular Complexes by Coarse-Grained
  Molecular Simulations. \\
  \textit{Acc. Chem. Res.}, \textbf{2015}, 48(12), 3026-3035.
\item Yunqiang Bian, \textbf{Cheng Tan}, Jun Wang, Yuebiao Sheng, Jian Zhang and
  Wei Wang. \\
  Atomistic Picture for the Folding Pathway of a Hybrid-1 Type Human Telomeric
  DNA G-Quadruplex. \\
  \textit{PLoS Comput. Biol.}, \textbf{2014}, 10(4), e1003562.
\item \textbf{Cheng Tan}, Wenfei Li and Wei Wang.\\
  Localized Frustration and Binding-Induced Conformational Change in Recognition
  of 5S RNA by TFIIIA Zinc Finger. \\
  \textit{J. Phys. Chem. B}, \textbf{2013}, 117(50), 15917--15925.
\item \textbf{Cheng Tan}, Wenfei Li, and Wei Wang.\\
  Specific Binding of a Short miRNA Sequence by Zinc Knuckles of Lin28: A
  Molecular Dynamics Simulation Study. \\
  \textit{J. Theor. Comput. Chem.}, \textbf{2013}, 12(8), 1341015.
\item Chunmei Lv, \textbf{Cheng Tan}, Meng Qin, Dawei Zou, Yi Cao, and Wei Wang.\\
  Low Folding Cooperativity of HP35 Revealed by Single-Molecule Force
  Spectroscopy and Molecular Dynamics Simulation. \\
  \textit{Biophys. J.}, \textbf{2012}, 102(8), 1944--1951.
\end{itemize}

%---------------------------------------------------------
\end{cventries}
